SPARQL on the Open, Decentralised Web

### 2016-08-03 dissertation/introduction.tex
mention writing RDF graphs #17

>>>>

More techniques have been developed for writing data. The simplest is
to write RDF in one of its serialisations to a file. Basic operations
like writing single triples or quads may be done with a framework
directly onto a triplestore. Since write operations are specified in
HTTP, write operations may use HTTP verbs if they are authorised to do
so. Finally, SPARQL has been extended with an update language in
version 1.1.
